Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-04-11 WSSSPE4_report/WSSSPE4_report.tex
fixing ñ in name

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Ray Idaszak$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nunez-Corrales$^{(9)}$,
Alice~Allen$^{(10)}$,
R.~Stuart~Geiger$^{(11)}$,
Jonah~Miller$^{(12)}$,
Emily~Chen$^{(13)}$,
Anshu~Dubey$^{(14)}$,
Wolfgang~Bangerth$^{(15)}$,
Patricia~Lago$^{(16)}$
%\\Author order to be determined based on contributions
}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Kyle~E.~Niemeyer$^{(2)}$,
Sandra~Gesing$^{(3)}$,
Lorraine~Hwang$^{(4)}$,
Simon~Hettrick$^{(5)}$,
Ray Idaszak$^{(6)}$,
Jean~Salac$^{(7)}$,
Neil~Chue~Hong$^{(8)}$,
Santiago~Nu\~nez-Corrales$^{(9)}$,
Alice~Allen$^{(10)}$,
R.~Stuart~Geiger$^{(11)}$,
Jonah~Miller$^{(12)}$,
Emily~Chen$^{(13)}$,
Anshu~Dubey$^{(14)}$,
Wolfgang~Bangerth$^{(15)}$,
Patricia~Lago$^{(16)}$
%\\Author order to be determined based on contributions
}
